---
title: "Edge angle project"
subtitle: "Import and format CSVs from GOM Inspect scripts"
author: "Ivan Calandra, Lisa Schunk"
date: "`r Sys.Date()`"
output:
  html_document:
    df_print: paged
    toc: true
    toc_depth: 3
    toc_float: true
    number_sections: true
    
---


```{r Knitr Options, include=FALSE}
	knitr::opts_chunk$set(comment = NA, message = FALSE, indent="", error = TRUE)
```

---


# Goal of the script
This script reads all CSV files exported from the GOM Inspect scripts, and imports them into one single CSV file and one single R file.  
The script will:

1. Read in the original CSV-files and put them together (step #3)  
2. Write an XLSX-file and save an R object ready for further analysis in R (step #4)

---

```{r}
dir_in <- "analysis/raw_data/EAP-flake"
dir_out <- "analysis/derived_data/"

```

Raw data must be located in `r paste0("~/", dir_in)`.  
Formatted data will be saved in `r paste0("~/", dir_out)`.

The knit directory for this script is the project directory.


---

# Load packages
```{r Libraries}
pack_to_load <- c("openxlsx", "R.utils")
sapply(pack_to_load, library, character.only = TRUE, logical.return = TRUE)

```


# Read in original CSV-files
## List all CSV-files
```{r}
Angles <- list.files(dir_in, pattern = "_w_.*\\.csv$", full.names = TRUE)
Angles.infos <- vector(mode = "list", length = length(Angles))
for (i in seq_along(Angles.infos)){
  Angles.infos[[i]] <- file.info(Angles[i])
}

Angles.infos <- do.call(rbind, Angles.infos)
Angles.infos <- data.frame(file = basename(row.names(Angles.infos)), Angles.infos)

```


# Read in the CSV-files
```{r}
Angles.data <- vector(mode = "list", length = length(Angles))
for (i in seq_along(Angles.data)){
  Angles.data[[i]] <- read.csv(Angles[i])
  Angles.data[[i]][["steps"]] <- Angles.data[[i]][2,3] - Angles.data[[i]][1,3]
}
Angles.data <- do.call(rbind, Angles.data)
names(Angles.data) <- c("section", "angle_number", "dist_intersection", "segment_length", "3points", "2lines", "best_fit", "steps")
Angles.data <- Angles.data[c(1:2, 8, 3:7)]
str(Angles.data)

```


# Extract units of all variables
The units are based on the first CSV-file.
Units are incorporated to the data object `Angles.data` as comments.

```{r}
headers <- unlist(strsplit(readLines(Angles[1], n = 1), ","))
units.var <- sub(pattern = ".*\\[(.+)\\]", "\\1", headers)[-(1:2)]
units.var <- c(rep(units.var[1],2), units.var[-1])
names(units.var) <- names(Angles.data)[-(1:2)]
comment(Angles.data) <- units.var
units.var.table <- data.frame(variable = names(units.var), unit = units.var)

```


---


# Save data
## Format name of output file
```{r}
file_out <- "EAP-flake"

```
The files will be saved as "`r paste0("~/", file_out, ".[ext]")`".


## Write to XLSX
```{r}
write.xlsx(list(data = Angles.data, units = units.var.table, CSV_infos = Angles.infos), 
           file = paste0(dir_out, file_out, ".xlsx"))

```


## Save R object
```{r}
saveObject(Angles.data, file = paste0(dir_out, file_out, ".Rbin"))

```

---

# sessionInfo() and RStudio version

```{r}
sessionInfo()

```

RStudio version `r readLines("analysis/scripts/RStudioVersion.txt", n = 1)`.


# Cite R packages used
```{r Citation}
for (i in pack_to_load) print(citation(i), bibtex = FALSE)

```


---


END OF SCRIPT
